simon_test_loop

### 2019-03-21 src/stack_test.Rmd
aic refix

betamval <- 0.25
mod9 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=0.25"), path = "../output/maxent/output/mod9foraic") 
mod9

@@

AIClist <- read.csv("../data/env/AICcCalculations.csv", header = TRUE)
for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

>>>>

AIClist <- read.csv("../data/env/AICcCalculations.csv", header = TRUE)

betamval <- 0.25
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=0.25"), path = "../output/maxent/output/mod9foraic")

#now based on glover-kapfer pdf with excel manual + https://esajournals.onlinelibrary.wiley.com/doi/full/10.1890/10-1171.1.... lets try automate some of this..

for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

betamval <- 0.50
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=0.50"), path = "../output/maxent/output/mod9foraic")

@@

for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

betamval <- 0.75
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=0.75"), path = "../output/maxent/output/mod9foraic")

for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

betamval <- 1
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=1"), path = "../output/maxent/output/mod9foraic")

for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

betamval <- 1.25
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=1.25"), path = "../output/maxent/output/mod9foraic")

for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

betamval <- 1.50
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=1.50"), path = "../output/maxent/output/mod9foraic")

for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

betamval <- 1.75
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=1.75"), path = "../output/maxent/output/mod9foraic")

for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

betamval <- 2
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=2"), path = "../output/maxent/output/mod9foraic")

for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

betamval <- 2.25
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=2.25"), path = "../output/maxent/output/mod9foraic")

for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

betamval <- 2.50
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=2.50"), path = "../output/maxent/output/mod9foraic")

for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

betamval <- 2.75
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=2.75"), path = "../output/maxent/output/mod9foraic")

for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

betamval <- 3
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=3"), path = "../output/maxent/output/mod9foraic")

for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

betamval <- 3.25
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=3.25"), path = "../output/maxent/output/mod9foraic")

for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

betamval <- 3.50
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=3.50"), path = "../output/maxent/output/mod9foraic")

for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

betamval <- 3.75
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=3.75"), path = "../output/maxent/output/mod9foraic")

for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred

betamval <- 4
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=4"), path = "../output/maxent/output/mod9foraic")

for (i in 1:nrow(AIClist)){
  if(AIClist$regularization[i] == betamval){
    AIClist$Test.AUC[i] <- testauc
    AIClist$Train.AUC[i] <- trainauc
    AIClist$n[i] <- notrainingpoints
    AIClist$coefficients[i] <- nocoeff
    AIClist$sum.of.logs[i] <- sumsamplepred
